\cvsection{Working Experience}
\begin{cventries}
  \cventry
    {Full Stack Engineer}
    {CSIS security Group A/S}
    {Copenhagen, Denmark}
    {Jan. 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {\url{https://www.csis.dk/}}
        \item {I am working as a part-time full stack developer in CSIS, the duty job includes designing database, building the API and frontend interface, writing unit test. DevOps is a rotating task for me, including new code deployment, maintaining and updating production/QA servers' environment}
	\item {The duty job for me also includes sometimes helping researchers implement analyzing and filtering dangerous  DNS/IP address, mainly using SVM(TensorFlow, Gaussian Kernel for SVM).}
      \end{cvitems}
    }
  \cventry
    {Image Processing Engineer}
    {Visztek Co.Ltd}
    {Shenzhen, China}
    {Jul. 2015 - Sep. 2016}
    {
      \begin{cvitems}
        \item {\url{http://www.visztek.com/en/index.html}}
        \item {Visztek Co.Ltd is one of leading companies which specializes in the development, production and sales of CAD/CAM software and equipment for the PCB industry.}
	\item {As an Image Processing Engineer, my duty job was mainly to analyze the scan of PCB and improve the existing algorithm for segmentation of PCB, detection of circuite on PCB(Based on OpenCV(C++).}
	\item {Besides researching job, I would also work on maintain and devlop production code(java/SDK).}
      \end{cvitems}
    }
  \cventry
    {Image Processing Engineer Intern}
    {Huawei}
    {Shenzhen, China}
    {Jan. 2015 - Jun. 2015}
    {
	\begin{cvitems}
	  \item {\url{http://www.huawei.com/en/}}
	  \item {Full-time Internship in Cloud Solution Department, Huawei}
	  \item {Working on Image Recognition Group. My daily work is to develop algorithms on Image Recognition, based on OpenCV(C++) and Machine Learning.}
	\end{cvitems}
    }
\end{cventries}
